Import_Map

### 2024-06-06 Code/Plots_ProNicheMap.Rmd
Add rainbow

```{r world map}
world_coordinates <- map_data("world")

# world_coordinates$facetsFuture <- 'Future~scenario'

@@

# PhotoperiodDepthFullO2$facetsFull <- 'Full Oxygen'
# PhotoperiodDepthOMZ$facetsOMZ <- 'Oxygen Minimum Zone'

NichesFullO2North <- PhotoperiodDepthFullO2 %>%
  filter(lat == 45) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 0) %>% 
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6.5)  +
  labs(title = "Full Oxygen") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
  coord_fixed(ratio = 2, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both, DayofYear = label_value)) +
  guides(color = "none") +
  theme_bw()+
  theme(plot.title = element_text(size = 22),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=20),
        #axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=18),
        #axis.title.y = element_text(vjust = 1),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14)) 
NichesFullO2North

NichesFullO2Equat <- PhotoperiodDepthFullO2 %>%
  filter(lat == 0) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 0) %>% 
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6.5)  +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
  coord_fixed(ratio = 2, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
  guides(color = "none") +
  theme_bw() +
  theme(plot.title = element_text(vjust = 10),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=20),
        #axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=18),
        #axis.title.y = element_text(vjust = 1),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))

@@

NichesOMZNorth <- PhotoperiodDepthOMZ %>%
  filter(lat == 45) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 0) %>% 
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6.5)  +
  labs(title = "Oxygen Minimum Zone") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
  coord_fixed(ratio = 2, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
  guides(color = "none") +
  theme_bw() +
  theme(plot.title = element_text(size = 22),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=20),
        #axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=18),
        #axis.title.y = element_text(vjust = 1),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))

@@

# PhotoperiodDepthOMZ1<-PhotoperiodDepthOMZ %>% 
# filter(DayofYear == "Summer Solstice")
# PhotoperiodDepthOMZ1$nm <- c(400, 400, 700, 700)
# PhotoperiodDepthOMZ1$de <- c(400, 400, 700, 700)
# 
# PhotoperiodDepthOMZ2<-PhotoperiodDepthOMZ %>% 
# filter(DayofYear == "Winter Solstice")
# PhotoperiodDepthOMZ2$nm <- c(400, 400, 700, 700)
# 
# PhotoperiodDepthOMZ3<-PhotoperiodDepthOMZ %>% 
# filter(DayofYear == "Equinox")
# PhotoperiodDepthOMZ3$nm <- c(400, 400, 700, 700)
# 
# PhotoperiodDepthOMZss<-rbind(PhotoperiodDepthOMZ1, PhotoperiodDepthOMZ2, PhotoperiodDepthOMZ3)

NichesOMZEquat <- PhotoperiodDepthOMZ %>%
  filter(lat == 0) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 0) %>%

ggplot()+
  # stat_wl_strip(aes(x = nm), ymin = "50 m", ymax = "100 m", alpha = 0.5, PhotoperiodDepthOMZss) +
  # scale_fill_identity() +
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6.5)  +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
  coord_fixed(ratio = 2, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
  guides(color = "none") +
  theme_bw() +
  theme(plot.title = element_text(vjust = 10),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=20),
        #axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=18),
        #axis.title.y = element_text(vjust = 1),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))

@@

@@

```{r}
#FUll
# world_coordinatesRainbow <- map_data("world")
world_coordinatesRainbow$nm <- c(400, 700)

data_text1 <- data.frame(label = c('~Clade~HLI'))
data_text2 <- data.frame(label = c('~Clade~HLI'))
data_text3 <- data.frame(label = c('~Clade~HLI'))

data_text4 <- data.frame(label = c('Deep~(30~µE~","~4~h):~Clade~LLIV'))
data_text5 <- data.frame(label = c('Deep~(30~µE~","~6~h):~Clades~HLI~","~LLII/III~","~LLIV'))
data_text6 <- data.frame(label = c('Deep~(30~µE~","~7~h):~Clades~HLI~","~LLII/III~","~LLIV'))
data_text7 <- data.frame(label = c('Deep~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))

```{r}
#Full
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
RainbowTropicFull<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 180, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_ellipse(aes(x0 = 555, y0 = 143, a = 170, b = 40, angle = pi / 20), fill = "white", colour = "white") +
  coord_fixed() +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(70, 230)) +
  geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
  geom_text(data=data_text2, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
  geom_text(data=data_text6, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
RainbowTropicFull

RainbowWinterFull<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
  coord_fixed() +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(70, 230)) +
    geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
  geom_text(data=data_text1, aes(x=400, y=230, label=label, hjust=0), size=4.5, parse=TRUE) +
  geom_text(data=data_text2, aes(x=400, y=220, label=label, hjust=0), size=4.5, parse=TRUE) +
  geom_text(data=data_text3, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
  geom_text(data=data_text4, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
  geom_text(data=data_text6, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
  geom_text(data=data_text7, aes(x=400, y=70, label=label, hjust=0), size=4.5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
RainbowWinterFull

>>>>

```{r world map}
world_coordinates <- map_data("world") 
# world_coordinates$facetsFuture <- 'Future~scenario'

@@

d=data.frame(x=c(-Inf,700,700), y=c(-Inf,-Inf,3), t=c('a', 'a', 'a'), r=c(1,2,3))

PhotoperiodDepthFullO2<-PhotoperiodDepthFullO2
PhotoperiodDepthFullO2$nm <- c(400, 400, 400, 400, 400, 400, 700, 700, 700, 700, 700, 700)

PhotoperiodDepthOMZ<-PhotoperiodDepthOMZ
PhotoperiodDepthOMZ$nm <- c(400, 400, 400, 400, 400, 400, 700, 700, 700, 700, 700, 700)

NichesFullO2North <- PhotoperiodDepthFullO2 %>%
  filter(lat == 45) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 400) %>% 
ggplot()+
  geom_point(aes(x = nm, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = Inf, alpha = 0.3, PhotoperiodDepthFullO2) +
  scale_fill_identity() +
  # scale_x_continuous(breaks=seq(0, 25, by = 5)) +
  # coord_cartesian(xlim = c(0, 20)) +
  coord_fixed(ratio = 55, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  #geom_ellipse(aes(x0 = 555, y0 = 1.43, a = 10, b = 2, angle = pi / 1), fill = "transparent", colour = "transparent") +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6.5)  +
  ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
  guides(color = "none") +
  labs(title = "Full Oxygen") +
  theme_bw() +
  theme(plot.title = element_text(size = 22),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=20),
        #axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=18),
        #axis.title.y = element_text(vjust = 1),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14)) 
NichesFullO2North

NichesFullO2Equat <- PhotoperiodDepthFullO2 %>%
  filter(lat == 0) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 400) %>% 
ggplot()+
  geom_point(aes(x = nm, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = Inf, alpha = 0.3, PhotoperiodDepthFullO2) +
  scale_fill_identity() +
  # scale_x_continuous(breaks=seq(0, 25, by = 5)) +
  # coord_cartesian(xlim = c(0, 20)) +
  coord_fixed(ratio = 55, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  #geom_ellipse(aes(x0 = 555, y0 = 1.43, a = 10, b = 2, angle = pi / 1), fill = "transparent", colour = "transparent") +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6.5)  +
  ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
  guides(color = "none") +
  theme_bw() +
  theme(plot.title = element_text(vjust = 10),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=20),
        #axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=18),
        #axis.title.y = element_text(vjust = 1),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))

@@

NichesOMZNorth <- PhotoperiodDepthOMZ %>%
  filter(lat == 45) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 400) %>% 
ggplot()+
  geom_point(aes(x = nm, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = Inf, alpha = 0.3, PhotoperiodDepthOMZ) +
  scale_fill_identity() +
  # scale_x_continuous(breaks=seq(0, 25, by = 5)) +
  # coord_cartesian(xlim = c(0, 20)) +
  coord_fixed(ratio = 55, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  #geom_ellipse(aes(x0 = 555, y0 = 1.43, a = 10, b = 2, angle = pi / 1), fill = "transparent", colour = "transparent") +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6.5)  +
  ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
  guides(color = "none") +
  labs(title = "Oxygen Minimum Zone") +
  theme_bw() +
  theme(plot.title = element_text(size = 22),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=20),
        #axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=18),
        #axis.title.y = element_text(vjust = 1),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))

@@

NichesOMZEquat <- PhotoperiodDepthOMZ %>%
  filter(lat == 0) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 400) %>%

ggplot()+
  geom_point(aes(x = nm, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = Inf, alpha = 0.3, PhotoperiodDepthOMZ) +
  scale_fill_identity() +
  # scale_x_continuous(breaks=seq(0, 25, by = 5)) +
  # coord_cartesian(xlim = c(0, 20)) +
  coord_fixed(ratio = 55, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  #geom_ellipse(aes(x0 = 555, y0 = 1.43, a = 10, b = 2, angle = pi / 1), fill = "transparent", colour = "transparent") +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6.5)  +
  ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
  guides(color = "none") +
  theme_bw() +
  theme(plot.title = element_text(vjust = 10),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=20),
        #axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=18),
        #axis.title.y = element_text(vjust = 1),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))

@@

```{r, fig.height = 8, fig.width = 16, warning = FALSE}

P1<-ggdraw() +
  draw_plot(NichesFullO2North, x = 0.001, y = 0.695, width = .36, height = .22) +
  draw_plot(NichesFullO2Equat, x = 0.001, y = 0.485, width = .36, height = .22) +
  draw_plot(map, x = .179, y = .2, width = 0.8, height = 0.8) 
P1

P2<-ggdraw() +
  draw_plot(NichesOMZNorth, x = 0.001, y = 0.695, width = .36, height = .22) +
  draw_plot(NichesOMZEquat, x = 0.001, y = 0.485, width = .36, height = .22) +
  draw_plot(map, x = .179, y = .2, width = 0.8, height = 0.8) 
P2

ggarrange(P1, P2, ncol = 1, nrow = 2)

ggsave(file = file.path(FigPath, paste("NichesMap_2",".png",sep = "")), height=18, width= 20,  dpi = 300, limitsize = TRUE)
```

```{r save plot}
ggsave(file = file.path(FigPath, paste("NichesMap_2",".png",sep = "")), height=8, width= 22,  dpi = 300, limitsize = TRUE)
```

---------------------------------------------------------------------------------------------------------------

# Plot the image
plot(1:width, type = "n", xlim = c(0, width), ylim = c(0, height),
     xlab = "", ylab = "", axes =FALSE)
rasterImage(DepthBackdrop, 0, 0, width, height)

#points(PhotoperiodDepthFullO2$PhoticperiodPeakSatPAR_h, PhotoperiodDepthFullO2$DepthNames)

@@

```{r}
world_coordinatesRainbowSurface <- map_data("world") 
world_coordinatesRainbowDepth <- map_data("world")

world_coordinatesRainbowSurface$nm <- c(400, 700)
world_coordinatesRainbowDepth$nm <- c(400, 550)

data_textSurface <- data.frame(label = c('Near~Surface~(180~µE)'))
data_textDepth <- data.frame(label = c('Deep~(30~µE)'))
```

```{r}
#Full
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
ddepth=data.frame(x=c(400,700,700), y=c(160,160,260), t=c('a', 'a', 'a'), r=c(1,2,3))

RainbowSurface<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 150, ymax = 200, alpha = 0.5, world_coordinatesRainbowSurface) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "red", show.legend = F) +
  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 40, angle = pi / 10), fill = "red", colour = "red") +
  #geom_ellipse(aes(x0 = 555, y0 = 143, a = 170, b = 40, angle = pi / 20), fill = "white", colour = "white") +
  coord_fixed() +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(70, 230)) +
  geom_text(data=data_textSurface, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
RainbowSurface

RainbowSurface1<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbowSurface) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  #geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
  coord_fixed() +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(70, 230)) +
  geom_text(data=data_textDepth, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
RainbowSurface1

RainbowDepth1<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 180, ymax = 200, alpha = 0.5, world_coordinatesRainbowDepth) +
  scale_fill_identity() +
  geom_polygon(data=ddepth, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  #geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
  #geom_ellipse(aes(x0 = 555, y0 = 143, a = 170, b = 40, angle = pi / 20), fill = "white", colour = "white") +
  coord_fixed() +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(70, 230)) +
  geom_text(data=data_textSurface, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
RainbowDepth1
